Response to the defense feedback

### 2021-06-16 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by the AFL and Valgrind, we use the bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset (Load Memory Address (LMA)) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the enclave code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the enclave image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

We rely on the program header and symbol information to recover the
offset in the binary. During the loading process, the operating system
maps each segment into a contiguous memory region. So the offset of
the virtual memory address between the code within the same segment is
the same as the offset within the binary file. We choose the start
address of some common functions (e.g., $\textsf{main}$) ($b$) as the navigation
function. We get the virtual memory address of the start of the
function ($\mathit{VMA}_b$) from the DBI tool and the load memory
address of the function ($\mathit{LMA}_b$) from the symbol
information. For any virtual address, we use Equation~\ref{equ:eq6} to
calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
\end{equation}

>>>>

\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by AFL and Valgrind, we use a bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset LMA (Load Memory Address) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

We rely on the program header and symbol information to recover the
offset in the binary. During the loading process, the operating system
maps each segment into a contiguous memory region. So the offset of
the virtual memory address between the code within the same segment is
the same as the offset within the binary file. We choose the start
address of some common functions (e.g., $\textsf{main}$) as the navigation
function. Let $b$ be the navigation function here. 
We get the virtual memory address of the start of the
function ($\mathit{VMA}_b$) from the DBI tool and the load memory
address of the function ($\mathit{LMA}_b$) from the symbol
information. For any virtual address, we use Equation~\ref{equ:eq6} to
calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
\end{equation}
